\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
new version of water box (based on the latest version of the abstract); whitespace to align bottom
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64955 15284696-431f-4ddb-bdfa-cd5b030d7da7

\begin{minipage}{0.5\linewidth}
\includegraphics[scale=0.5]{images/summer_mean_temp_slope.pdf}
The linear regression slope computed with t.rast.series of the temperate climate zone in the European Union
for summer season from 1950 - 2011 (Gebbert and Pebesma, 2014 \cite{Gebbert20141}). Red color
indicates rising temperature, blue indicates falling temperature. Units are degree Celsius per year.
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
\includegraphics[scale=1.25]{images/Seasonal_temperature_trend_Europe_1950_2010.pdf}
Seasonal mean temperature trend for the temperate climate zone of the European Union
(Gebbert and Pebesma, 2014 \cite{Gebbert20141}). The modules \gmodule{t.rast.aggregate},
\gmodule{t.rast.univar} and the open source statistical software system R
were used to create this plot.
\end{minipage}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Natural Hazards: Water, Floods and Erosion}}{
GRASS GIS entails several modules that constitute the result of active research on 
natural hazard. The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b}) 
for overland flow under rainfall excess conditions was integrated into the Emergency 
Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}). 
It was also modified by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of a 
specialised software called \textit{Tangible Landscape} (previously \textit{Tangible GIS}), which also 
incorporated the \gamodule{r.damflood} module.\newline\linebreak

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{rsimwater_architects}
Overland flow used for landscape architecture design in Tangible Landscape environment
\end{minipage}
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{damflood_tangible}
Coal ash pond breach in Tangible Landscape environment using \gamodule{r.damflood} module
\end{minipage}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Evapotranspiration (ET)}}{
With the various types of actual ET models being developed in the last 20 years, 
it becomes necessary to inter-compare methods. Most of already published ETa models 
comparisons address few number of models, and small to medium areas 
(Chemin, 2014 \cite{chemin2012distributed}; Gao and Long, 2008 \cite{gao2008intercomparison}; 
Garcia et al., 2007 \cite{garcia2007comparison}; Suleiman et al., 2008
\cite{suleiman2008intercomparison}; Timmermans et al., 2007 \cite{timmermans2007intercomparison}). 
With the large amount of remote sensing data covering the Earth, and the daily 
information available for more than twelve years (i.e. Aqua/Terra-MODIS) for each pixel 
location, it becomes paramount to have a more complete comparison, 
in space and time.
\newline

@@

To address this new experimental requirement, a distributed computing framework was 
designed and created (Chemin, 2012 \cite{chemin2012distributed}). 
The architecture design was built from original satellite datasets to various levels 
of processing until reaching the requirement of various ETa models input dataset. 
Each input product is computed once and reused in all ETa models requiring such input. 
This permits standardization of inputs as much as possible to zero-in variations of 
models to the models internals/specificities. All of the ET models are available in the 
new GRASS GIS version 7 as imagery modules and replicability is complete for future 
research.
}

>>>>

\vspace*{1cm}

\begin{minipage}{0.5\linewidth}
\includegraphics[scale=0.5]{images/summer_mean_temp_slope.pdf}
The linear regression slope computed with t.rast.series of the temperate climate zone in the European Union
for summer season from 1950 - 2011 (Gebbert and Pebesma, 2014 \cite{Gebbert20141}). Red color
indicates rising temperature, blue indicates falling temperature. Units are degree Celsius per year.
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
\includegraphics[scale=1.25]{images/Seasonal_temperature_trend_Europe_1950_2010.pdf}
Seasonal mean temperature trend for the temperate climate zone of the European Union
(Gebbert and Pebesma, 2014 \cite{Gebbert20141}). The modules \gmodule{t.rast.aggregate},
\gmodule{t.rast.univar} and the open source statistical software system R
were used to create this plot.
\end{minipage}

\vspace*{1cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Natural Hazards: Water, Floods and Erosion}}{

GRASS GIS entails several modules that constitute the result of active research on natural hazard.
The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b})
for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}).
The module \gmodule{r.sim.water} together with
the module \gmodule{r.sim.sediment} for erosion-deposition modeling
implements path sampling algorithm which is robust and easy to parallelize.
The \gmodule{r.sim.water} module was also utilized by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of
\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
a dam break inundation simulation \cite{cannata2012two}.

\vspace*{1cm}

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{rsimwater_architects}
Overland flow used for landscape architecture design in Tangible Landscape environment
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{damflood_tangible}
Coal ash pond breach in Tangible Landscape environment using \gamodule{r.damflood} module
\end{minipage}

\vspace*{1.4cm}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Evapotranspiration (ET)}}{
With the various types of actual ET models being developed in the last 20 years, 
it becomes necessary to inter-compare methods. Most of already published ETa models 
comparisons address few number of models, and small to medium areas 
(Chemin, 2014 \cite{chemin2012distributed}; Gao and Long, 2008 \cite{gao2008intercomparison}; 
Garcia et al., 2007 \cite{garcia2007comparison}; Suleiman et al., 2008
\cite{suleiman2008intercomparison}; Timmermans et al., 2007 \cite{timmermans2007intercomparison}). 
With the large amount of remote sensing data covering the Earth, and the daily 
information available for more than twelve years (i.e. Aqua/Terra-MODIS) for each pixel 
location, it becomes paramount to have a more complete comparison, 
in space and time.

\vspace*{1cm}

@@

To address this new experimental requirement, a distributed computing framework was 
designed and created (Chemin, 2012 \cite{chemin2012distributed}). 
The architecture design was built from original satellite datasets to various levels 
of processing until reaching the requirement of various ETa models input dataset. 
Each input product is computed once and reused in all ETa models requiring such input. 
This permits standardization of inputs as much as possible to zero-in variations of 
models to the models internals/specificities. All of the ET models are available in the 
new GRASS GIS version 7 as imagery modules and replicability is complete for future 
research.

\vspace*{0.6cm}
